\phantomsection

\vspace*{2.5cm}

This master thesis presents the work of the student Pierre Ecarlat at National Institute of Informatics, Tokyo. This project has been done as an internship for six months, from the 8\textsuperscript{th} of February to the 3\textsuperscript{rd} of August 2016, and aims to validate his engineering studies in IT, Robotics, and Artificial Intelligence.

This project has been done in collaboration with four other engineers, and has, as goal, to do real-time semantic segmentation on aerial views (drone-derived data) using Deep Learning methods. The whole project includes the comparison of multiple Deep Learning architectures according to various criteria, the creation of an open-source framework implementing various learning methods for these architectures, facilitating the comparison, and the implementation of the selected architecture in a drone. All of these points have allowed me to reuse what I have learnt during my studies, and made me more confident in my engineering skills.

A presentation of this work will be given on the 19\textsuperscript{th} of September, in Paris, for my engineering school in IT and Robotics - represented by Mr. Louis Jouanny as president of the jury and Mr. François Bouchet as tutor -. My master in Artificial Intelligence is also invited to attend - represented by Mr. Nicolas Bredeche as tutor -. Mr. Helmut Prendinger will also attend the presentation, as supervisor of the project, expert in the related research field, and as representative of National Institute of Informatics, which hosted me during this internship.